### 2024-03-06 supporting.tex
Fixed sizing of scores_histogram figure in supporting.tex to make consistent with other figures
Added hierarchy_mu figure to supporting.tex

\begin{figure}[h!]
\includegraphics[width=0.75\textwidth]{scores/out/scores_histogram.png}
\centering
\caption{\textbf{Histogram of disorder score rates in regions.}
The grey interval indicates the upper decile of the distribution across both disorder and order regions, which was used as the input set for the GO term enrichment analysis.}
\label{sfig:scores_histogram}
\end{figure}

@@

>>>>

\begin{figure}[h!]
\includegraphics[width=6in]{scores/out/scores_histogram.png}
\centering
\caption{\textbf{Histogram of disorder score rates in regions.}
The grey interval indicates the upper decile of the distribution across both disorder and order regions, which was used as the input set for the GO term enrichment analysis.}
\label{sfig:scores_histogram}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy_mu_OU.png}
\centering
\caption{\textbf{Hierarchical clustering of normalized optimal values.}
The optimal values of the OU model ($\mu_{OU}$) are clustered with the same method as the signatures derived from the log likelihood ratios in Fig~\ref{fig:hierarchy}. The optimal values are expressed as $z$-scores relative to each feature distribution in the subset of rapidly evolving disorder regions. Values below or above negative or positive three are indicated with magenta and cyan, respectively.}
\label{sfig:hierarchy_mu}
\end{figure}
